%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
 \cventry
    {Personal Project} % Role
    {Telegram Group Manager} % Event
    {} % Location
    {January,2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A Telegram Bot for managing the official Codex group.}
        \item {Greets a new member on joining the telegram group and sends them the group rules and other important links.}
        \item {Built in fetcher for xkcd comics.}
        % \item {Server always running}
        \item {Technologies Used: Python, Telegram Api, Heroku deployment}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Team Project} % Role
    {Radical} % Event
    {} % Location
    {October,2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A price notifier extension for Chrome browser.(for Flipkart and Amazon)}
        \item {The price and product information is retrieved by scraping the product page and a database is used to store both the information about the client and their products and prices.}
        % \item {The prices and product information is retrieved by scraping the product page.}
        \item {Notifies a user when the price drops by sending an email.}
        \item The user can also specify a threshold which in turn only notifies when the price drops below it.
        \item {Technologies Used: JavaScript, HTML5, CSS3, PHP, MySQL}
      \end{cvitems}
    }

%---------------------------------------------------------
%   \cventry
%     {Personal Project} % Role
%     {Movie Search App} % Event
%     {} % Location
%     {December,2018} % Date(s)
%     {
%       \begin{cvitems} % Description(s)
%         \item {Get details of all movies related to the keyword entered during search}
%         \item {The user can create an account and add any movie to his/her watch-list}
%         \item {Technologies Used: HTML5, Node.js}
%       \end{cvitems}
%     }

%---------------------------------------------------------
 \cventry
    {Personal Project} % Role
    {MPEX(Mini Project Expander)} % Event
    {} % Location
    {Ongoing} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A project expander and descriptor for developers using Git.}
        \item {UI based python application which keeps track of all the sources used and also custom notes by the user that are input into it. Also provides a simple ui based interface for various Git commands.}
        \item {Stores the data in text file created along with the project by the app or specified by the user.}
        % \item{Also provides a simple ui based interface for various git commands}
        \item {Technologies Used: Python, Git}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
